A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-18 paper/elsarticle/elsarticle-template.tex
moved

Using the $X$- and $Y$-axes of an image of the scene as a proxy, our contribution is to propose a system that produces the effect of keystone correction analytically, and in a manner aligning the axes of the augmentation with those of the proxy image. We achieve this by distorting the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (i) facing directly downwards to the scene plane and (ii) rotated to place the axes of the image plane of the virtual projector in line with those of the camera. This enables intuitive placement of augmentations in the scene, and eliminates the need for manual keystone correction. Moreover, our system is able to handle a projector equipped with a steerable mirror without need for explicitly modeling the action of the steerable mirror on the projector.

@@

@@

The problem of correcting for distortions as outlined in Section~\ref{sec:intro} requires knowledge of the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene, and the geometry of the scene itself within at least the projector’s field of view, as illustrated in Figure 1. This is because the scene point `illuminated' by a pixel in the projector's image plane is given by intersecting its corresponding ray with the geometry of the scene surface. To model this interaction calls for a one-time camera-projector calibration, which includes recovery of the scene plane. Next, the relative camera-projector-scene plane geometry is used to compute a plane-induced homography.

The hardware setup employed

\subsection{Camera-projector Calibration}

@@

@@

\subsection{Correcting for Distortion}

@@

@@

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

>>>>

Using the $X$- and $Y$-axes of an image of the scene as a proxy, our contribution is to propose a system that produces the effect of keystone correction analytically, and in a manner aligning the axes of the augmentation with those of the proxy image. We achieve this by distorting the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (i) facing directly downwards to the scene plane and (ii) rotated to place the axes of the image plane of the virtual projector in line with those of the camera. This enables intuitive placement of augmentations in the scene, and eliminates the need for manual keystone correction. Moreover, a consequence of our approach is that our system is able to handle a projector equipped with a steerable mirror without need for explicitly modeling the action of the steerable mirror on the projector.

@@

todo - maybe Majesa would like to help?

@@

The problem of correcting for distortions as outlined in Section~\ref{sec:intro} requires knowledge of the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene (i.e., we must `calibrate' the projector) and the geometry of the scene itself (i.e., we must recover the scene plane) within at least the projector's field of view. This is because the scene point `illuminated' by a pixel in the projector's image plane is given by intersecting its corresponding ray with the geometry of the scene surface. To model this interaction calls for (i) a one-time projector calibration, which in our approach calls for additionally calibrating a camera overlooking the scene and includes recovery of the scene plane as a convenient side effect. Next, (ii) the relative camera-projector-scene plane geometry is used to compute a plane-induced homography that distorts the image to be projected in a manner that it appear undistorted to the viewer, and placed in alignment with the axes of a proxy image of the scene. These to points are treated in Sections~\ref{sec:approach:geometry} and \ref{sec:approach:homography}, respectively.

\subsection{Recovering Geometry}\label{sec:approach:geometry}

The `output' of projector (or camera) calibration is a mathematical model that determines, for each pixel xproj in the projector's (or camera's) image plane πproj, the ray from the projector’s center of projection Cproj through xproj, along which the pixel is projected to the scene. Inversely, the model also determines the projection $\mathbf{x}'_\text{proj}$ of any point $\mathbf{X}'_\text{proj}$ in the scene to the projector's (or camera's) image plane $\mathbf{\pi}_\text{proj}$, obtained by intersecting $\mathbf{\pi}_\text{proj}$ with the ray from $\mathbf{C}_\text{proj}$ through $\mathbf{X}'_\text{proj}$. Such a model is said to function in accordance with the principle of central projection.

Notably, central projection is the same principle that underlies the modeling of conventional cameras. A camera modeled in accordance with the principle of central projection is called a pinhole camera. A pinhole camera can be expressed in terms of a $3~\times~3$ camera calibration matrix $\mathtt{K}$,  derived from the camera's focal length and principal point. In practice, a pinhole camera model works well in modeling how the respective rays through the pixels of the image plane fan out into the scene, on the condition that images to which the model is applied have been corrected for lens distortions caused by the camera’s lens system. The `output' of camera calibration is accordingly not only the matrix $\mathtt{K}$, but the associated lens distortions model coefficients as well. The lens distortion model coefficients enable applying a lens distortion model to undistort any image acquired by the camera.

In practice, calibrating a camera relies on (i) establishing 2D-3D correspondences between pixels in the camera's image plane and corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that outputs the calibration matrix $\mathtt{K}$ and the associated distortion model coefficients. Calibration of a projector can be carried out in precisely the same manner insofar as step (ii) is concerned; the major difference in projector calibration relative to camera calibration concerns the manner in which 2D-3D correspondences are identified, i.e., between pixels in the image plane of the projector and the corresponding points in the scene.

@@

\paragraph{Scene plane recovery}

@@

\subsection{Correcting for Distortion}\label{sec:approach:homography}

@@

todo - maybe Hans would like to help?

@@
